The Spatial and Temporal Domains of Modern Ecology

### 2017-06-28 paper/SI.tex
Final submitted version (amended from previous to revise institutional affiliation and add links to code and data for reviewers)

\usepackage{scicite}
\usepackage{times}
\usepackage{graphicx}
\usepackage{lineno}
\usepackage{longtable}
%\usepackage{multicolumn}
\usepackage[skip=2pt,font=normalsize]{caption}
\usepackage[LGRgreek]{mathastext}
\usepackage{multirow}

@@

The following text provides additional information on this study's Methods and Results.  The full manuscript, data, and code used to analyze the data are available on an accompanying github repository (https://github.com/ecohydro/ecoscales). \textbf{Note to editors and reviewers: this repository is currently private, but will be transitioned to a public repository upon acceptance of manuscript.}

>>>>

\usepackage{scicite}
\usepackage{times}
\usepackage{graphicx}
\usepackage{lineno}
\usepackage{longtable}
%\usepackage{multicolumn}
\usepackage[skip=2pt,font=normalsize]{caption}
\usepackage[LGRgreek]{mathastext}
\usepackage{multirow}
\usepackage[
  breaklinks=true,
  colorlinks=true,
  linkcolor=blue,anchorcolor=blue,
  citecolor=blue,filecolor=blue,
  menucolor=blue,pagecolor=blue,
  urlcolor=blue]{hyperref}

@@

The following text provides additional information on this study's Methods and Results.  The full manuscript, data, and code are available on an accompanying \href{https://github.com/ecohydro/ecoscales}{github repository}. \textbf{Note to editors and reviewers: this repository is currently private, but will be made public upon acceptance of manuscript. In the interim, the code and data can be downloaded from the following links}:
\href{https://www.dropbox.com/s/4r9h8mn1wa4kjsn/calibration.html?dl=0}{Calibration analysis}; \href{https://www.dropbox.com/s/n0zq5zufu96ktfl/calibration-set.xlsx?dl=0
}{Calibration dataset}; \href{https://www.dropbox.com/s/bzni8dhqy8un4fz/space-time.html?dl=0
}{Main analysis}; \href{https://www.dropbox.com/s/vujjo2x4f5kwqkb/main-results.xlsx?dl=0
}{Main dataset}

### 2017-06-28 paper/main.tex
Final submitted version (amended from previous to revise institutional affiliation and add links to code and data for reviewers)

\author
{Lyndon Estes$^{\ast1, 2, 3}$, Paul R. Elsen$^{1, 4}$, Tim Treuer$^{5}$, Labeeb Ahmed$^{6}$, \\
Kelly Caylor$^{1, 7}$, Jason Chang$^{6}$, Jonathan J. Choi$^{5}$, and Erle Ellis$^{6}$ \\
\\
\normalsize{$^{1}$Woodrow Wilson School, Princeton University, Princeton, NJ 08544, USA}\\
\normalsize{$^{2}$Civil and Environmental Engineering, Princeton University, Princeton, NJ 08544, USA}\\
\normalsize{$^{3}$Graduate School of Geography, Clark University, Worcester MA 01610, USA}\\
\normalsize{$^{4}$Department of Environmental Science, Policy, and Management,}\\
\normalsize{University of California Berkeley, Berkeley, CA 94720, USA}\\
\normalsize{$^{5}$Ecology and Evolutionary Biology, Princeton University, Princeton, NJ 08544, USA}\\
\normalsize{$^{6}$Geography and Environmental Systems, University of Maryland Baltimore County,}\\ 
\normalsize{Baltimore, MD 21250, USA}\\
\normalsize{$^{7}$Earth Research Institute, University of California Santa Barbara, Santa Barbara, CA 93106, USA}\\
\\
\normalsize{$^\ast$To whom correspondence should be addressed; E-mail:  LEstes@clarku.edu.}}
% Include the date command, but leave its argument blank.

>>>>

\author
{Lyndon Estes$^{\ast1, 2, 3}$, Paul R. Elsen$^{2, 4}$, Tim Treuer$^{5}$, Labeeb Ahmed$^{6}$, \\
Kelly Caylor$^{3, 7}$, Jason Chang$^{6}$, Jonathan J. Choi$^{5}$, and Erle Ellis$^{6}$ \\
\\
\normalsize{$^{1}$Graduate School of Geography, Clark University, Worcester MA 01610, USA}\\
\normalsize{$^{2}$Woodrow Wilson School, Princeton University, Princeton, NJ 08544, USA}\\
\normalsize{$^{3}$Civil and Environmental Engineering, Princeton University, Princeton, NJ 08544, USA}\\
\normalsize{$^{4}$Department of Environmental Science, Policy, and Management,}\\
\normalsize{University of California Berkeley, Berkeley, CA 94720, USA}\\
\normalsize{$^{5}$Ecology and Evolutionary Biology, Princeton University, Princeton, NJ 08544, USA}\\
\normalsize{$^{6}$Geography and Environmental Systems, University of Maryland Baltimore County,}\\ 
\normalsize{Baltimore, MD 21250, USA}\\
\normalsize{$^{7}$Earth Research Institute, University of California Santa Barbara, Santa Barbara, CA 93106, USA}\\
\\
\normalsize{$^\ast$To whom correspondence should be addressed; E-mail:  LEstes@clarku.edu.}}
% Include the date command, but leave its argument blank.
